Math 462 Project

### 2025-02-25 writing/462 Project _Stochastic.tex
Add feedback on the stochastic model write-up.

@@

@@

@@

@@

@@

>>>>

\medskip

% COMMENTS BEGIN HERE
\color{red}

Shouldn't the binding equation use $\overline{D}_{P}$ (i.e. the delta concentration in neighbouring cells) instead of $D_{P}$? Also, I think this would be a good place to state the assumptions you used to derive these equations. The start of section "2. The Model" in Collier et al. contains some more information about interpreting $N$ and $D$ that might be useful to read through.

\medskip

I'm also unsure about the activation equation, because it implies that a complex is splitting to form an $N_{P}^{*}$ (what makes this different from $N_{P}$, by the way?) and a $D_{P}$. I think something like $C_{P} \xrightarrow{k_{2}} N_{P}^{*} + D_{P}$ might be more accurate.

\color{black}
% COMMENTS END HERE

\medskip

@@

% COMMENTS BEGIN HERE
\color{red}

I think there are a couple mistakes in this equation. For example, in the first term, we're looking at the probability of a binding event, which creates one $C_{P}$ and destroys a $N_{P}$ and a $D_{P}$. Therefore, I believe we need to be in state $(N_{P} + 1, D_{P} + 1, C_{P} - 1)$  in order for a binding event to take us to state $(N_{P}, D_{P}, C_{P})$. I think the first term should be the following, although I could be mistaken.

$$
k_{1} (N_{P} + 1)(D_{P} + 1) P(N_{P} + 1, D_{P} + 1, C_{P} - 1, t)
$$

\medskip

I think some of the other terms have similar issues. I'm also still unsure about the difference between the unbinding ($k_{-1}$) and activation ($k_{2}$) reactions. What assumptions are you making?

\color{black}
% COMMENTS END HERE

@@

% COMMENTS BEGIN HERE
\medskip
\color{red}
This looks good and makes sense to me.
\color{black}
\medskip
% COMMENTS END HERE

@@

% COMMENTS BEGIN HERE
\medskip
\color{red}
I'm not sure how you got to here, but the equation makes sense.
\color{black}
\medskip
% COMMENTS END HERE

@@

% COMMENTS BEGIN HERE
\medskip
\color{red}
Isn't this just the previous equation without the $k_{-1}$? I also think you're missing an $E[C_{P}]$:

$$
\frac{dE[C_{P}]}{dt} = k_{1}E[N_{P}]E[D_{P}] - (k_{-1} + k_{2})E[C_{P}] - k_{-1}E[C_{P}]
$$

and then you can do some simple algebra to get rid of the last term.
\color{black}
\medskip
% COMMENTS END HERE

@@

% COMMENTS BEGIN HERE
\medskip
\color{red}
Where does this equation come from?
\color{black}
\medskip
% COMMENTS END HERE
